Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/relwk.tex
done with relwk pass

@@

The second class is logic errors, where application code misinterprets input data. Safe languages
and exploit mitigation technologies do not help against such vulnerabilities. This can lead to
serious security consequences when two systems disagree on the meaning of a network packet or a
signed message, as in iOS\footnote{The XNU kernel and the user code-signing verifier interpret
  executable metadata differently, so the code signature sees different bytes at a virtual address
  than the executable that runs.}~\cite{evaders6} and Android~\cite{saurik-masterkey}code signing
and even the X.509 protocol underlying SSL~\cite{DBLP:conf/fc/KaminskyPS10}. Logic errors are often
causing memory corruption bugs as well, for example when a protocol stores the size of a buffer in
two places and the implementation does not check their consistency. These mistakes are
highly application-specific, and are difficult to mitigate using existing techniques, and these
mistakes can occur even in high-level languages that guarantee memory safety. By allowing developers
to specify their data format just once, Nail avoids logic errors and inconsistencies in parsing and
output generation.

@@

Proper input recognition has been shown to be an excellent way of eliminating ambiguous inputs. In
one case, a PDF parser implemented in Coq could eliminate over $95\%$ of known malicious
PDFs~\cite{Bogk-PDF}. The same project also produced a ``counter-example'' PDF that triggered
numerous bugs in other PDF parsers. However, manually writing parser code and proving unambiguity
does not scale to the number of file formats and protocols in existence and might result in parser
code tied to one specific application.

\paragraph{Workshop paper}
We presented an early design of Nail at the LangSec workshop~\cite{bangert:nail-langsec} that had
no support for transformations, as described in Section~\ref{s:transforms}, and much more limited
dependent fields, as described in Section~\ref{s:dependent}. With our extended and refined design,
Nail can support much more complicated, real-world data formats.
%%This is supposed to go into design
% While it is possible to express short transformations on the input
% entirely as semantic actions\footnote{This is in fact the design
% rationale, to perform computation on the fly as the parser walks the
% parse tree.}, more complicated programs usually construct an internal
% representation, which contains all relevant information from the input
% in a format native to the programming language used. For example, a C
% programmer ideally wants to deal with structs and NULL-terminated arrays,
% whereas a C++ programmer might expect STL containers, a Java programmer
% interfaces, a Haskell programmer records and a LISP programmer property
% lists.  The structure of this internal representation usually resembles
% the structure of the grammar.

>>>>

We presented an earlier design of Nail at a
workshop~\cite{bangert:nail-langsec-anon}.  At that stage, Nail had only
limited support for dependent fields, and did not support stream
transforms at all, which are crucial for supporting real-world formats
like DNS and Zip.  The workshop paper also did not provide a detailed
design discussion or evaluation.

@@

The second class is logic errors, where application code misinterprets
input data. Safe languages and exploit mitigation technologies do not
help against such vulnerabilities. This can lead to serious security
consequences when two systems disagree on the meaning of a network
packet or a signed message.  For example, the XNU kernel in iOS and the
user code-signing verifier interpret executable metadata differently,
so the code signature sees different bytes at a virtual address than the
executable that runs~\cite{evaders6}.  Android's code signing system also
had a vulnerability due to parsing ambiguities~\cite{saurik-masterkey},
and parsing ambiguities even contributed to attacks on the X.509 protocol
underlying SSL~\cite{DBLP:conf/fc/KaminskyPS10}.  Logic errors can also
cause memory corruption bugs as well, for example when a protocol stores
the size of a buffer in two places and the implementation does not check
their consistency. These mistakes are highly application-specific, and
are difficult to mitigate using existing techniques, and these mistakes
can occur even in high-level languages that guarantee memory safety. By
allowing developers to specify their data format just once, Nail avoids
logic errors and inconsistencies in parsing and output generation.

@@

Proper input recognition has been shown to be an excellent way of
eliminating ambiguous inputs.  In one case, a PDF parser (implemented
in Coq) could eliminate over $95\%$ of known malicious PDFs by checking
whether they conform to the PDF format~\cite{Bogk-PDF}. The same project
also produced a ``counter-example'' PDF that triggered numerous bugs
in other PDF parsers. However, manually writing parser code and proving
unambiguity does not scale to the number of file formats and protocols
in existence and might result in parser code tied to one specific
application. By supporting a wide range of real-world file formats,
Nail helps programmers produce precise parsers for complex grammars.

%%This is supposed to go into design
% While it is possible to express short transformations on the input
% entirely as semantic actions\footnote{This is in fact the design
% rationale, to perform computation on the fly as the parser walks the
% parse tree.}, more complicated programs usually construct an internal
% representation, which contains all relevant information from the input
% in a format native to the programming language used. For example, a C
% programmer ideally wants to deal with structs and NULL-terminated arrays,
% whereas a C++ programmer might expect STL containers, a Java programmer
% interfaces, a Haskell programmer records and a LISP programmer property
% lists.  The structure of this internal representation usually resembles
% the structure of the grammar.
